Data processing

### 2024-05-23 scripts/data_processing.qmd
commenting the file and minor corrections

```{r}
# these two files come from the ALFAM2 Zenodo repository (https://zenodo.org/records/8109634)
data_interval_level = read.csv (file = "../data/ALFAM2_interval.csv")
data_plot_level = read.csv (file = "../data/ALFAM2_plot.csv")

# these two files come from the supplementary material of Hafner et al (2019)
calibration_subset_pmids = read.csv (file = "../data/1-s2.0-S1352231018308069-mmc1.csv")
evaluation_subset_pmids = read.csv (file = "../data/1-s2.0-S1352231018308069-mmc2.csv")

@@

@@

@@

@@

@@

@@

```{r}
quartiles_climatic_variable
```

@@

```{r}
quartiles_plot_level_variable
```

@@

## data_scenarios_random_forest
```{r}
data_scenarios_random_forest = data_scenarios %>% 
    select (- pmid, - group_temp, - group_wind, - group_rain) %>%

    mutate (man.source = as.numeric (recode (man.source, "pig" = 1, "cat" = 0))) %>%
    mutate (app.mthd = as.numeric (recode (app.mthd, "bc" = 1, "ts" = 2, "os" = 3, "bsth" = 4))) %>%
    mutate (incorp = as.numeric (recode (incorp, "none" = 1, "shallow" = 2, "deep" = 3))) %>%

@@

@@

    mutate (man.source = as.numeric (recode (man.source, "pig" = 1, "cat" = 0))) %>%
    mutate (app.mthd = as.numeric (recode (app.mthd, "bc" = 1, "ts" = 2, "os" = 3, "bsth" = 4))) %>%
    mutate (incorp = as.numeric (recode (incorp, "none" = 1, "shallow" = 2, "deep" = 3))) %>%

@@

@@

    mutate (incorp.shallow = ifelse (incorp == "shallow", 1, 0)) %>%
    mutate (incorp.deep = ifelse (incorp == "deep", 1, 0)) %>%
    select (- incorp)
    # ---------

@@

@@

    pivot_longer (cols = c (10 : 27), names_to = c (".value", "time"), names_pattern = "(.+)_(.+)") %>%

>>>>

Construction of the data_alfam2 dataframe.

```{r}
# these two files come from the ALFAM2 Zenodo repository (https://zenodo.org/records/8109634)
data_interval_level = read.csv (file = "../data/Hafner_et_al_2019/ALFAM2_interval.csv")
data_plot_level = read.csv (file = "../data/Hafner_et_al_2019/ALFAM2_plot.csv")

# these two files come from the supplementary material of Hafner et al (2019)
calibration_subset_pmids = read.csv (file = "../data/Hafner_et_al_2019/1-s2.0-S1352231018308069-mmc1.csv")
evaluation_subset_pmids = read.csv (file = "../data/Hafner_et_al_2019/1-s2.0-S1352231018308069-mmc2.csv")

@@

Construction of the dama_ml dataframe.

@@

Construction of the data_random_forest dataframe.

@@

Construction of the data_xgboost dataframe.

@@

Construction of the data_lasso dataframe.

@@

Construction of the data_scenarios dataframe.

@@

```{r}
quartiles_climatic_variable %>% round (digits = 1)
```

@@

```{r}
quartiles_plot_level_variable %>% round (digits = 1)
```

@@

## data_scenarios_random_forest

Construction of the data_scenarios_random_forest dataframe.

```{r}
data_scenarios_random_forest = data_scenarios %>% 
    select (- pmid, - group_temp, - group_wind, - group_rain) %>%

    mutate (man.source = as.numeric (recode (man.source, "pig" = 1, "cat" = 0))) %>%
    mutate (app.mthd = as.numeric (recode (app.mthd, "bc" = 1, "ts" = 2, "os" = 3, "bsth" = 4))) %>%
    mutate (incorp = as.numeric (recode (incorp, "none" = 1, "shallow" = 2))) %>%

@@

Construction of the data_scenarios_xgboost dataframe.

@@

    mutate (man.source = as.numeric (recode (man.source, "pig" = 1, "cat" = 0))) %>%
    mutate (app.mthd = as.numeric (recode (app.mthd, "bc" = 1, "ts" = 2, "os" = 3, "bsth" = 4))) %>%
    mutate (incorp = as.numeric (recode (incorp, "none" = 1, "shallow" = 2))) %>%

@@

Construction of the data_scenarios_lasso dataframe.

@@

    mutate (incorp.shallow = ifelse (incorp == "shallow", 1, 0)) %>%
    mutate (incorp.deep = 0) %>%
    select (- incorp)
    # ---------

@@

Construction of the data_scenarios_alfam2 dataframe.

@@

    pivot_longer (cols = contains ("temp_") | contains ("wind_") | contains ("rain_"), names_to = c (".value", "time"), names_pattern = "(.+)_(.+)") %>%
